
\subsection{Dynamic Workers}
In the context of federated learning, the participating workers are more likely to be mobile phones and embedded devices, which are often not connected to a power supply and stable network. Thus the workers in FL system are highly dynamic and unstable, and they can join and exit the federation at any time. 

Traditional distributed systems adopt the heartbeat packet and time threshold to check the status of the workers. However, these methods are not applicable with the FL system for the next two reasons: 1) The server has to maintain the heartbeat connection with all the participating workers which limits the scalability of the system. 2) The computation times of each worker vary significantly due to the difference in the computing devices and network environment.

Fortunately, the design of \sys allows us to solve this problem decently. If the worker exits accidentally, the pulling requests it sends to other workers can be canceled immediately when the target workers find it unreachable. For those workers who have requested segments from the offline worker, they can monitor the status of the target workers, and once they see the connection with the target worker is lost, they can mark it as offline, resend the request to another worker and stop pulling from the offline worker. If it is a false report due to the network fluctuation or the offline worker comes back, the offline flag can be removed as long as the communication is reestablished. 

The participation of a new worker is relatively easy to handle. When a new worker comes to the federation, it first requests a worker list either from a server or an old worker. Then it pulls the segments and aggregates them as normal only without its own local model. With the aggregation result, it can start the training with its local dataset. When it sends the pulling requests to the target workers, the target worker adds the newcomer to the worker list. Since the new worker sends the pull requests to many workers in a single iteration, its existence will be quickly noticed by all other workers, and then the new worker successfully joins the federation.